\chapter*{Conclusion}
The process of designing, developing, and shipping this web application was overall successful, although there are still some parts that could be improved or extended in the future. However, our system is ready for these changes and we have learned valuable lessons along the way.

In particular, the design and development process was not as straightforward as we had initially anticipated. Instead, it was an iterative process that required close collaboration with the system requester. The stages of iteration were roughly as follows:

\begin{enumerate}
\item Problem description and basic page layout programming (homepage, cup, user, club).
\item Formalization of the model and proper division of code into system objects and task functions.
\item Analysis of user and club data, additional pages for categorization purposes.
\item Addition of regions for further extensible hierarchization.
\item Major final refactoring of the database, backend, and testing with dummy data insertion and querying.
\item Cloud readiness, Docker image of the web application, and Kubernetes deployment.
\end{enumerate}

In the future, the system can be extended by adding new public pages, statistical queries, and administrative tasks. These modifications might involve adding new pages, adjusting the model, or making minor design changes. Thanks to the divided code, these changes can be easily accommodated and will reside in the project GitHub repository \footnote{\url{https://github.com/KlosStepan/SwimmPair-Www}}.

Overall, we are pleased with the outcome of this project and look forward to seeing it evolve further in the future.
\addcontentsline{toc}{chapter}{Conclusion}

